### 2024-09-12 documentation/supplement.tex
updated article, pdfs, README

{
\centering\Large\textbf{Supplemental Online Material} 
}
\newline\newline
This supplemental material to the article ``TWINKLE: An open-source two-photon microscope for teaching and research'' describes the assembly, function and alignment of all parts of the microscope. Technical specifications are provided through the CAD files and the Zemax simulations in the online repository.

@@

\subsection{Miscellaneous tools}
\begin{itemize}
    \item Use a high quality duster to remove any residue from optical surfaces. We use a Miller-Stephenson Aero-Duster Ultra MS-222L.
    \item To glue optical filters we used an extra fast setting epoxy (Hardman Double/Bubble Epoxy). To seal small gaps, we use black silicone putty (V-tie self-setting silicone rubber).
    \item We used either McMaster or Thorlabs screwdrivers and hex keys.
    \item For alignment, we used laser viewing cards (VRC4, Thorlabs), cage system alignment plates (VRC4CPT, Thorlabs), and irises (SM1 Graduated Ring-Actuated Iris Diaphragm, SM1D12C, Thorlabs).
\end{itemize}

@@

\subsection{Parts and bill-of-materials}
All custom metal pieces are parts of the CAD assembly of the microscope. Ours were manufactured from Aluminium stock in the university machine shop, but other materials are possible. Aluminium has the added benefit of anodization, which can help control stray light. For example, if the microscope was used in a Virtual Reality system, we would anodize the collection optics to reduce scattering from the projector's light.\newline
An overview of the microscope's cost is shown in Tab.~\ref{tab_costs}. Keep in mind that these prices can significantly change over time, while some products can become unobtainable and need to be replaced with a different or newer model.
%
\begin{table}
\begin{center}
  \begin{tabular}{ l c r } \hline
   \textbf{Item} & \textbf{Info} & \textbf{Cost} \\ \hline
\rowcolor{gray!20} 920 nm fs-pulsed Laser  & Spark Alcor 920 + Warranty & 90 k \\
                   ScanImage DAQ-System \& optimized PC & Vidrio & 20 k \\
\rowcolor{gray!20} Piezo collar & Physik Instrumente & 16 k	\\
            $2\times$ PMTs + preamplifiers  & Hamamatsu \& Thorlabs & 12 k \\
\rowcolor{gray!20} Pockels cell             & Conoptics &	11 k \\
                   Objective                & Nikon &  8 k \\
\rowcolor{gray!20} Machining custom parts   & Machine Shop; as per CAD files &  7 k \\
                   Optical filters          & AVR optics \& Semrock &  7 k \\
\rowcolor{gray!20} Lenses + optomechanics   & Thorlabs \& Newport &  7 k \\
                   Galvo-Resonant Scanner set & Novanta &  6 k \\
\rowcolor{gray!20} Electronics/cables/tools & Newark \& McMaster &  5 k \\
                   Mounting rack            & Emcor Enclosures &  3 k \\
\rowcolor{gray!20} Laser shutter            & Uniblitz/Vincent &  2 k \\
                   Laser safety goggles     & Edmund Optics &  1 k \\
\rowcolor{gray!20} Laser power meter        & Coherent &  1 k \\
                   Agarose \& fluorescent beads     & Thermofisher &  1 k \\
  \hline
 \textbf{Total}                    & & \textbf{197 k} \\
  \hline
  \end{tabular}
\end{center}
\caption{\textbf{Overview of the approximate cost in 2024-US\$} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies. This is just a summary. The detailed bill-of-materials is provided in the git repository.}\label{tab_costs}
\end{table}

@@

    \item \textbf{H)} Two beam blocks (LB1, Thorlabs). Confirm that the right beam block terminates the waste beam leaving the Pockels cell. The left beam is used for calibrating the Pockels cell in ScanImage (the control software used by our microscope \cite{Vidrio2022, Pologruto2003}), together with a light sensor (I).

@@

    \item \textbf{K)} $2\times$ Beam Expander ($2\times$ Achromatic Galilean Beam Expander, GBE02-B, Thorlabs, inside SM1RC, Thorlabs). This expands the beam sufficiently to fill the apertures of the subsequent optics. Aligning the beam expander requires two steps. First, it has to be aligned to the optical axis. Second, it is critical that the beam stays collimated after the beam expander. For the first alignment, we use two irises, one screwed in the front, and one (on a reasonably long SM1 extension tube) behind the expander. The beam expander has to be positioned such that the irises cut into the beam symmetrically. Then, the expander is on-axis. Next, we need to adjust the collimation of the beam so that the beam is the same size at the exit and after a long distance using several mirrors, see Fig.~\ref{sfig3}. For optimal alignment, adjust the dial on the beam expander until it no convergence or divergence is visible.
    %
    \begin{SCfigure}
        \includegraphics[width=.5\textwidth]{sfig3.jpg}
      \caption{{\bf Method for making sure the beam is collimated.} Using a set of mirrors, the beam (yellow line) can be reflected back and fourth to increase the distance travelled. Along this path (in this example of $\approx 2.5\text{ m}$), the beam must not change size ($<1\text{ mm}$). This is validated with an IR detection card and switching between the forward and return path of the beam. This method allows to control beam divergence after the $2\times$ telescope to below 1 mrad.}
      \label{sfig3}
    \end{SCfigure}
    %
\item \textbf{L)} Iris (SM1D12C inside CP08, both Thorlabs) Used to check alignment.

\item \textbf{M)} Mirror (PF10-03-P0, Thorlabs, inside KCB1) to reflect the beam up at a right angle. For the next steps (in particular finding the optimal scanning mirror position), it is important that the beam travels up perpendicular to the optical table, and parallel to the 95 mm optical rail column that holds the scanning mirrors (next section).

@@

Following beam conditioning on the optical table, the beam is reflected up from the optical table towards the ceiling into a box housing the scanning mirrors. This is shown in Fig.~\ref{sfig4}. Following the scanning mirrors, the beam travels up through the scan lens, and directed to the microscope head with another mirror.
%
\begin{figure}[h]
    \includegraphics[width=\textwidth]{sfig4.jpg}
    \caption{{\bf Overall view of the scanning post.} \textbf{A)} Side few. Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components. Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labelled (E). \textbf{B)} Frontal view. The PMT preamplifiers (component G) and the scanning mirror power supply (component H) are visible.}
    \label{sfig4}
\end{figure}
%
%
\begin{enumerate}[]
    \item \textbf{A)} Mirror (BPF10-03-P0, inside KCB1, with CP12 attached) - turn the beam at a right angle.
    \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs). A detailed description is provided below.
    \item \textbf{D)} Empty tubing.
    \item \textbf{E)} Scan lens - See detailed description below.
    \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs). While we used a round 2 inch mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs). This increases the field-of-view because the cross-section of an ellipse at 45 degrees is a circle. At low magnification, a round mirror will lead to vignetting.
    \item \textbf{G)} PMT preamplifier (TIA60, Thorlabs) attached to a 95 mm rail.
    \item \textbf{H)} Power supply for the scanning mirrors (part of the Novanta scanning mirror set) housed in an electronics prototype box.
\end{enumerate}

@@

\begin{itemize}
    \item First, mount the 95 mm rail to the table. Then attach a bracket to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}). For alignment with cage systems, we use a cage system alignment plate (VRC4CPT, Thorlabs). The rest of the assembly here will be done without any lenses. The goal is a well-aligned beam that travels through the middle of all parts, and parallel to the optomechanical surfaces.
    \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}). To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}) facing up. These two pieces meet in the air. Sliding a finger across the small gap between the two pieces makes misalignment easy to notice haptically. Mount the box housing the scanning mirrors such that you can not feel the transition from the lower SM1 tubing to the upper SM1 tubing.
    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}) so that light travels through the center of the scanning mirrors and up the 95 mm rail. This is done with irises. One is attached at the entry port of the scanning mirror box, e.g. in the SM1 tube (component B in Fig.~\ref{sfig4}). Another two irises are attached, as far away as possible, to a 95 mm rail bracket. It is convenient to use the future holder of the scan lens (component D/E in Fig.~\ref{sfig4}). This ensures that the beam will pass through the center of the scan lens. As the mirror (component F in Fig.~\ref{sfig4}) is not installed yet, an IR detection card can conveniently be taped to the ceiling to make sure that the beam is on-axis. Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 Volt to position the mirror at its origin point. This can be done through the voltage supply, or to a good approximation through ScanImage by setting the scan mode to the highest possible zoom level. In our microscope design, it can be helpful to wiggle the lid to which the scanning mirrors are mounted (item C in Fig.~\ref{sfig4}). This step is tricky and can require some patience. 
    \item When confirmed that the light travels parallel to the 95 mm rail, we attach the mirror (component F in Fig.~\ref{sfig4}), and slide it along the cage rods to a position where the beam is reflected centrally through the caging system and the mount positioned on top of the 95 mm rail. This is done using the same set of two SM2-mounted irises that we used to make sure that light leaves the scanning mirror box without x or y displacement. The beam is now ready to travel through the microscope head.
\end{itemize}

@@

\begin{itemize}
    \item Mount the two 95 mm posts to the table.
    \item Mount the collection optics box to the Aluminium stage, and then mount the stage to the 95 mm rail. Do not install the photomultiplier tubes yet. These devices are light sensitive, and more alignment needs to be done before we are ready to install them.
    \item Equip the Aluminium stage with brackets and cage mounts to hold SM2 tubing (A, D and E in Fig.~\ref{sfig5}).
    \item First, we position the big mirror at a $45^\circ$ angle (component B in Fig.~\ref{sfig5}). Place two irises after the big mirror, one at the future position of the tube lens (component C in Fig.~\ref{sfig5}) and one far away beyond the future position of the collection mirror (component F in Fig.~\ref{sfig5}). Aligning the big mirror is fiddly, but can be achieved with small adjustments of its position in x and y, and the tilt of its housing. We found it helpful to use a 45 degree angled rod to guide the mirror in the direction parallel to its surface. Whichever method is used, this step can take some time. Importantly, do not adjust the set screws of the mirror on the scanning post (component F in Fig.~\ref{sfig4}) because that is already aligned.
    \item Install the collection mirror (component F in Fig.~\ref{sfig5}). Then position an iris in place of the future objective, and one as far away as possible just above the optical table. Shift the mirror along the rail and adjust its tilt via the set screws so that the beam is aligned with the two irises.
\end{itemize}

@@

    \item Before starting, make sure the lens groups in the tube and scan lens assembly are mounted correctly. Specifically, when inserted into one of our previously aligned SM2 mounting rings, they should focus the beam, but must not incur a lateral or angular displacement. To test this, one can screw them into component E in Fig.~\ref{sfig4}, and observe the beam far away on a wall. The lens groups must not change the position of this spot, only its size. Only proceed if the lens groups were assembled and mounted correctly.
    \item The first lens group to be installed is the tube lens assembly. Position the tube lens such that the beam, at maximum zoom level, is focused at the back-aperture plane of the objective. As the objective is not installed yet, an IR detection card can be placed at its future location. We designed the microscope such that the tube lens assembly is to be mounted on a 1 inch long SM2 extension to the cage plates (Component D in Fig.~\ref{sfig5}. See also the diagram in the section on ``Tube lens Assembly'' below). Observe how the focal plane changes when moving the tube lens along the optical rails (component E in Fig.~\ref{sfig4}). When its correct position is confirmed, tighten the set screws on the optical cage.
    \item Next, install the scan lens above the scanning mirror box. The spacing between tube lens and scan lens is critical because the beam leaving the tube lens has to be collimated. To test this, remove the elliptical mirror (component F in Fig.~\ref{sfig4}) from its housing, and observe the spot on a wall far away, while moving the scan lens up and down on the 95 mm optical rail. Find a position at which the beam neither converges, nor diverges after the tube lens, and the spot on the wall has the same size as the beam right after the tube lens. Only then is the beam well collimated. Clamp down the scan lens on its rail.
    \item Next, reinstall the elliptical mirror (component F in Fig.~\ref{sfig4}), and observe the back-aperture of the objective, while moving the scanning mirror box up and down. The scan mirrors have to be positioned in so that they are conjugated to the back aperture of the objective. It is positioned correctly when the well-collimated light converges on the back aperture of the objective across scan angles. Make sure that (1) no beam clipping is visible on high zoom along the optical path. (2) In the conjugated plane of the scan lens, a nice and crisp plane should be visible on an IR card, produced by the scanning beams focused down to a point. (3) The fast resonant scan combined with the slow scan gives the beam a visible dynamic, a ``wobble''. If the scanning mirror box is positioned correctly, then, the beam at the objective back aperture will not translate while scanning because all deflection angles converge on the back aperture (cf. Fig. 1 in the main manuscript). In other words, the ``wobble'' becomes minimal at the plane conjugated to the scan mirrors. Notice how adjustment of the scan mirrors relative to the scan lens can bring this conjugate plane to any point below the collection optics. Now, adjust the height of the scanning mirror box to a point so that the minimal-wobble plane is located at the back aperture of the objective and clamp down the scanning mirror box. For a useful illustration of this method, see also \cite{Yao2023}. Of note, this step of fine-tuning the position of the scan box up and down along the 95 mm optical rail is the reason why we stressed the importance of the alignment of the scanning post, the components A in Fig.~\ref{sfig3} and M in Fig.~\ref{sfig1} earlier. It was critical that across the various heights used here, the scanning mirror box was precisely aligned with the beam.

@@

\subsubsection{PMT installation}
PMTs are light sensitive. Always store them with their aperture covered with black tape when not in use. When removing the tape for installation, this installation into the collection box must be done in darkness and as quickly as possible. We recommend to use black silicone putty (V-tie self setting silicone rubber), and have it ready for use to seal the gap between the PMTs and the aluminium box. Switch the room lights off, wait a few minutes to adapt to the darkness then mount the PMTs on their respective ports.

\subsection{Shield the light path}
Now that your microscope is ready, finish shielding the light path with SM1 and SM2 tubing, and cover the optical table with sheet metal. We use bent Aluminium sheet, placed on small columns made from T-slotted rail.

@@

\begin{itemize}
    \item Place the first element on top of the spanner wrench (Thorlabs SPW604) using lens paper. Check the lens thoroughly. Dust can be blown away with a duster, finger prints wiped off with Methanol and a lens cleaning tissue (cf. Fig.~\ref{sfig8}B).
    \item Blow it with the air duster. 
    \item Slide the SM2L10 tube over the element until it sits in the end. Sometimes it needs to be wiggled, but do not force it.
    \item Flip the whole thing over.
    \item Now the element is in the tube. Tighten it with a SM2 retaining ring.
    \item Insert a second SM2 retaining ring for spacing. 
    \item Repeat the previous steps to install the second lens above the SM2 retaining ring
    \item Flip again, blow with air, and set the lens in place with a third SM2 retaining ring. This produces the configuration shown in Fig.~\ref{sfig8}A.
    \item Be careful with dust and fingerprints when putting elements into the tube. Confirm that there are no fingerprints, and no dust particles trapped on or between the lenses.
\end{itemize}
%
Our simulations indicate that the lens spacing between the two doublets is not critical, and the approximate clearance provided by two SM2 spacer rings is sufficient. This is shown in Fig.~\ref{sfig8}A. For more precise placement, a spacer ring like the one shown in Fig.~\ref{sfig8}B can be used. This will be important for the slightly more complex scan lens assembly described in the next section.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig8.jpg}
    \caption{{\bf Assembly of lens groups.} \textbf{A)} Tube lens assembly with the two doublets held in place with spacer rings. \textbf{B)} Assembly method of lenses: Lenses and spacer rings are stacked on a SM2 spanner, ready for the SM2 tubing to be lowered around them. \textbf{C)} Design of the scan lens assembly. Notice the custom spacer rings in blue. The distance between the last element of the scan lens assembly and the scanning mirror box is $\approx 1.35 \text{ inches}$. \textbf{D)} The assembled scan lens group in its SM2 housing.}
    \label{sfig8}
\end{figure}
%
\subsection{Scan lens assembly}

>>>>

{
\centering\Large\textbf{Supplemental Online Material} 
}
\newline\newline
This supplemental material to the article ``TWINKLE: An open-source two-photon microscope for teaching and research'' describes the assembly, function and alignment of all parts of the microscope. Technical specifications are provided through the CAD files and the Zemax simulations in the online repository at \url{https://github.com/BrainCOGS/Microscope}.

@@

\subsection{Miscellaneous tools}
\begin{itemize}
    \item Use a high quality duster to remove any residue from optical surfaces. We use a Miller-Stephenson Aero-Duster Ultra MS-222L, in addition to lens tissues (MC-5, Thorlabs) and Methanol (Sigma-Aldrich).
    \item To glue optical filters we used an extra fast setting epoxy (Hardman Double/Bubble Epoxy). To seal small gaps, we use black silicone putty (V-tie self-setting silicone rubber).
    \item We used either McMaster or Thorlabs screwdrivers and hex keys.
    \item For alignment, we used laser viewing cards (VRC4, Thorlabs), cage system alignment plates (VRC4CPT, Thorlabs), and irises (SM1 Graduated Ring-Actuated Iris Diaphragm, SM1D12C, Thorlabs).
\end{itemize}

@@

\subsection{Parts and bill-of-materials}
All custom metal pieces are parts of the CAD assembly of the microscope. Ours were manufactured from aluminium stock in the university machine shop, but other materials are possible. Aluminium has the added benefit of anodization, which can help control stray light. For example, if the microscope was used in a Virtual Reality system, we would anodize the collection optics to reduce scattering from the projector's light.\newline
An overview of the microscope's cost is shown in Tab.~\ref{tab_costs}. Keep in mind that these prices can significantly change over time, while some products can become unobtainable and need to be replaced with a different or newer model.
%
\begin{table}
\begin{center}
  \begin{tabular}{ l c r } \hline
   \textbf{Item} & \textbf{Info} & \textbf{Cost} \\ \hline
\rowcolor{gray!20} 920 nm fs-pulsed Laser  & Spark Alcor 920 + Warranty & 90 k \\
                   ScanImage DAQ-System \& optimized PC & Vidrio & 20 k \\
\rowcolor{gray!20} Piezo collar & Physik Instrumente & 16 k	\\
            $2\times$ PMTs + preamplifiers  & Hamamatsu \& Thorlabs & 12 k \\
\rowcolor{gray!20} Pockels cell             & Conoptics &	11 k \\
                   Objective                & Nikon &  8 k \\
\rowcolor{gray!20} Machining custom parts   & Machine Shop; as per CAD files &  7 k \\
                   Optical filters          & AVR optics \& Semrock &  7 k \\
\rowcolor{gray!20} Lenses + optomechanics   & Thorlabs \& Newport &  7 k \\
                   Galvo-Resonant Scanner set & Novanta &  6 k \\
\rowcolor{gray!20} Electronics/cables/tools & Newark \& McMaster &  5 k \\
                   Mounting rack            & Emcor Enclosures &  3 k \\
\rowcolor{gray!20} Laser shutter            & Uniblitz/Vincent &  2 k \\
                   Laser safety goggles     & Edmund Optics &  1 k \\
\rowcolor{gray!20} Laser power meter        & Coherent &  1 k \\
                   Agarose \& fluorescent beads     & Thermofisher &  1 k \\
  \hline
 \textbf{Total}                    & & \textbf{197 k} \\
  \hline
  \end{tabular}
\end{center}
\caption{\textbf{Overview of the approximate cost in 2024-US\$} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies. This is just a summary. The detailed bill-of-materials is provided in the git repository.}\label{tab_costs}
\end{table}

@@

    \item \textbf{H)} Two beam blocks (LB1, Thorlabs). Confirm that the right beam block terminates the rejected beam leaving the Pockels cell. The left beam block is used for calibrating the Pockels cell in ScanImage (the control software used by our microscope \cite{Vidrio2022, Pologruto2003}), together with a light sensor (I).

@@

    \item \textbf{K)} $2\times$ Beam Expander ($2\times$ Achromatic Galilean Beam Expander, GBE02-B, Thorlabs, inside SM1RC, Thorlabs). This expands the beam sufficiently to fill the apertures of the subsequent optics. Aligning the beam expander requires two steps. First, it has to be aligned to the optical axis. Second, it is critical that the beam stays collimated after the beam expander. For the first alignment, we use two irises, one screwed in the front, and one (on a reasonably long SM1 extension tube) behind the expander. The beam expander has to be positioned such that the irises cut into the beam symmetrically. Then, the expander is on-axis. Next, we need to adjust the collimation of the beam so that the beam is the same size at the exit and after a long distance using several mirrors, see Fig.~\ref{sfig3}. For optimal alignment, adjust the dial on the beam expander until it no convergence or divergence is visible.
    %
    \begin{SCfigure}
        \includegraphics[width=.5\textwidth]{sfig3.jpg}
      \caption{{\bf Method for making sure the beam is collimated.} Using a set of mirrors, the beam (yellow line) can be reflected back and fourth to increase the distance travelled. Along this path (in this example of $\approx 2.5\text{ m}$), the beam must not change size ($<1\text{ mm}$). This is validated with an IR detection card and switching between the forward and return path of the beam. This method allows to control beam divergence after the $2\times$ telescope to below 1 mrad.}
      \label{sfig3}
    \end{SCfigure}
    %
\item \textbf{L)} Iris (SM1D12C inside CP08, both Thorlabs) used to check alignment.

\item \textbf{M)} Mirror (PF10-03-P0, Thorlabs, inside KCB1) to reflect the beam up at a right angle. For the next steps (in particular finding the optimal scanning mirror position), it is important that the beam travels up perpendicularly to the optical table, and parallel to the 95 mm optical rail column that holds the scanning mirrors (next section).

@@

Following beam conditioning on the optical table, the beam is reflected up from the optical table towards the ceiling into a box housing the scanning mirrors. This is shown in Fig.~\ref{sfig4}A,B. Following the scanning mirrors, the beam travels up through the scan lens, and directed to the microscope head with another mirror.
%
\begin{figure}[h]
    \includegraphics[width=\textwidth]{sfig4.jpg}
    \caption{{\bf Overall view of the scanning post.} \textbf{A)} Side few. Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components. Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labelled (E). \textbf{B)} Frontal view. The PMT preamplifiers (component G) and the scanning mirror power supply (component H) are visible.}
    \label{sfig4}
\end{figure}
%
%
\begin{enumerate}[]
    \item \textbf{A)} Mirror (BPF10-03-P0, inside KCB1, with CP12 attached) - turn the beam at a right angle.
    \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs). A detailed description is provided below.
    \item \textbf{D)} Empty tubing.
    \item \textbf{E)} Scan lens - See detailed description below.
    \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs). While we used a round 2 inch mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs). This increases the field-of-view because the cross-section of an ellipse at 45 degrees is a circle. At low magnification, a round mirror will lead to vignetting.
    \item \textbf{G)} PMT preamplifier (TIA60, Thorlabs) attached to a 95 mm rail.
    \item \textbf{H)} Power supply for the scanning mirrors (part of the Novanta scanning mirror set) housed in an electronics prototype box.
\end{enumerate}

@@

\begin{itemize}
    \item First, mount the 95 mm rail to the table. Then attach a bracket to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}). For alignment with cage systems, we use a cage system alignment plate (VRC4CPT, Thorlabs). The rest of the assembly here will be done without any lenses. The goal is a well-aligned beam that travels through the center of all parts, and parallel to the optomechanical surfaces.
    \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}). To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}) facing up. These two pieces meet in the air. Sliding a finger across the small gap between the two pieces makes misalignment easy to notice haptically. Mount the box housing the scanning mirrors such that you can not feel the transition from the lower SM1 tubing to the upper SM1 tubing.
    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}A) so that light travels through the center of the scanning mirrors and up the 95 mm rail. This is done with irises. One is attached at the entry port of the scanning mirror box, e.g. in the SM1 tube (component B in Fig.~\ref{sfig4}A). Another two irises are attached, as far away as possible, to a 95 mm rail bracket. It is convenient to use the future holder of the scan lens (component D/E in Fig.~\ref{sfig4}). This ensures that the beam will pass through the center of the scan lens. As the mirror (component F in Fig.~\ref{sfig4}) is not installed yet, an IR detection card can conveniently be taped to the ceiling to make sure that the beam is on-axis. Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 Volt to position the mirror at its origin point. This can be done through the voltage supply, or to a good approximation through ScanImage by setting the scan mode to the highest possible zoom level. In our microscope design, it can be helpful to wiggle the lid to which the scanning mirrors are mounted (item C in Fig.~\ref{sfig4}). This step is tricky and can require some patience. 
    \item When confirmed that the light travels parallel to the 95 mm rail, we attach the mirror (component F in Fig.~\ref{sfig4}), and slide it along the cage rods to a position where the beam is reflected centrally through the caging system and the mount positioned on top of the 95 mm rail. This is done using the same set of two SM2-mounted irises that we used to make sure that light leaves the scanning mirror box without x or y displacement. The beam is now ready to travel through the microscope head.
\end{itemize}

@@

\begin{itemize}
    \item Mount the two 95 mm posts to the table.
    \item Mount the collection optics box to the aluminium stage, and then mount the stage to the 95 mm rail. Do not install the photomultiplier tubes yet. These devices are light sensitive, and more alignment needs to be done before we are ready to install them.
    \item Equip the aluminium stage with brackets and cage mounts to hold SM2 tubing (A, D and E in Fig.~\ref{sfig5}).
    \item First, we position the big mirror at a $45^\circ$ angle (component B in Fig.~\ref{sfig5}). Place two irises after the big mirror, one at the future position of the tube lens (component C in Fig.~\ref{sfig5}) and one far away beyond the future position of the collection mirror (component F in Fig.~\ref{sfig5}). Aligning the big mirror is fiddly, but can be achieved with small adjustments of its position in x and y, and the tilt of its housing. We found it helpful to use a 45 degree angled rod to guide the mirror in the direction parallel to its surface. Whichever method is used, this step can take some time. Importantly, do not adjust the set screws of the mirror on the scanning post (component F in Fig.~\ref{sfig4}) because that is already aligned.
    \item Install the collection mirror (component F in Fig.~\ref{sfig5}). Then position an iris in place of the future objective, and a second iris as far away as possible just above the optical table. Use an adapter with external $\text{M}32\times0.75$ threads and internal SM1 threads (SM1A33, Thorlabs) to attach the irises to the objective collar. Then shift the collection mirror along the rail and adjust its tilt via the set screws so that the beam is aligned with the two irises.
\end{itemize}

@@

    \item Before starting, make sure the lens groups in the tube and scan lens assembly are mounted correctly. Specifically, when inserted into one of our previously aligned SM2 mounting rings, they should focus the beam, but must not incur a lateral or angular displacement. To test this, one can screw them into component E in Fig.~\ref{sfig5}, and observe the beam far away on a wall. The lens groups must not change the position of this spot, only its size. Only proceed if the lens groups were assembled and mounted correctly.
    \item The first lens group to be installed is the tube lens assembly. Position the tube lens such that the beam, at maximum zoom level, is focused at the back-aperture plane of the objective. As the objective is not installed yet, an IR detection card can be placed at its future location. We designed the microscope such that the tube lens assembly is to be mounted on a 1 inch long SM2 extension to the cage plates (Component D in Fig.~\ref{sfig5}. See also the diagram in the section on ``Tube lens Assembly'' below). Observe how the focal plane changes when moving the tube lens along the optical rails (Component E in Fig.~\ref{sfig5}). When its correct position is confirmed, tighten the set screws on the optical cage.
    \item Next, install the scan lens above the scanning mirror box. The spacing between tube lens and scan lens is critical because the beam leaving the tube lens has to be collimated. To test this, remove the elliptical mirror (component F in Fig.~\ref{sfig5}) from its housing, and observe the spot on a wall far away, while moving the scan lens up and down on the 95 mm optical rail. Find a position at which the beam neither converges, nor diverges after the tube lens, and the spot on the wall has the same size as the beam right after the tube lens. Only then is the beam well collimated. Clamp down the scan lens on its rail.
    \item Next, reinstall the elliptical mirror (component F in Fig.~\ref{sfig5}), and observe the back-aperture of the objective, while moving the scanning mirror box up and down. The scan mirrors have to be positioned in so that they are conjugated to the back aperture of the objective. It is positioned correctly when the well-collimated light converges on the back aperture of the objective across scan angles. Make sure that (1) no beam clipping is visible on high zoom along the optical path. (2) In the conjugated plane of the scan lens, a nice and crisp plane should be visible on an IR card, produced by the scanning beams focused down to a point. (3) The fast resonant scan combined with the slow scan gives the beam a visible dynamic, a ``wobble''. If the scanning mirror box is positioned correctly, then, the beam at the objective back aperture will not translate while scanning because all deflection angles converge on the back aperture (cf. Fig. 1 in the main manuscript). In other words, the ``wobble'' becomes minimal at the plane conjugated to the scan mirrors. Notice how adjustment of the scan mirrors relative to the scan lens can bring this conjugate plane to any point below the collection optics. Now, adjust the height of the scanning mirror box to a point so that the minimal-wobble plane is located at the back aperture of the objective and clamp down the scanning mirror box. For a useful illustration of this method, see also \cite{Yao2023}. Of note, this step of fine-tuning the position of the scan box up and down along the 95 mm optical rail is the reason why we stressed the importance of the alignment of the scanning post, the components A in Fig.~\ref{sfig4} and M in Fig.~\ref{sfig1} earlier. It was critical that across the various heights used here, the scanning mirror box was precisely aligned with the beam.

@@

\subsubsection{PMT installation}
PMTs are light sensitive. Always store them with their aperture covered with blackout tape when not in use (AT205-1.0 black aluminium foil tape, Thorlabs). When removing the tape for installation, this installation into the collection box must be done in darkness and as quickly as possible. We recommend to use black silicone putty (V-tie self setting silicone rubber), and have it ready for use to seal the gap between the PMTs and the aluminium box. Switch the room lights off, wait a few minutes to adapt to the darkness then mount the PMTs on their respective ports.

\subsection{Shield the light path}
Now that your microscope is ready, finish shielding the light path with SM1 and SM2 tubing, and cover the optical table with sheet metal. We use bent aluminium sheet, placed on small columns made from T-slotted rail.

@@

\begin{itemize}
    \item Place the first element on top of the spanner wrench (Thorlabs SPW604) using lens paper. Check the lens thoroughly. Dust can be blown away with a duster, finger prints wiped off with Methanol and a lens cleaning tissue.
    \item Blow it with the air duster. 
    \item Slide the SM2L10 tube over the element until it sits in the end. Sometimes it needs to be wiggled, but do not force it.
    \item Flip the whole thing over.
    \item Now the element is in the tube. Tighten it with a SM2 retaining ring.
    \item Insert a second SM2 retaining ring for spacing. 
    \item Repeat the previous steps to install the second lens above the SM2 retaining ring
    \item Flip again, blow with air, and set the lens in place with a third SM2 retaining ring. This produces the configuration shown in Fig.~\ref{sfig8}A.
    \item Be careful with dust and fingerprints when putting elements into the tube. Confirm that there are no fingerprints, and no dust particles trapped on or between the lenses.
\end{itemize}
%
Our simulations indicate that the lens spacing between the two doublets is not critical, and the approximate clearance provided by two SM2 spacer rings is sufficient. This is shown in Fig.~\ref{sfig8}A. For more precise placement, a spacer ring like the one shown in Fig.~\ref{sfig8}B can be used. This will be important for the slightly more complex scan lens assembly described in the next section.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig8.jpg}
    \caption{{\bf Assembly of lens groups.} \textbf{A)} Tube lens assembly with the two doublets held in place with spacer rings. \textbf{B)} Assembly method of lenses: Lenses and spacer rings are stacked on a SM2 spanner, ready for the SM2 tubing to be lowered around them. \textbf{C)} Design of the scan lens assembly. Notice the custom spacer rings in blue. The distance between the last element of the scan lens assembly and the scanning mirror box is $\approx 1.35 \text{ inches}$. \textbf{D)} The assembled scan lens group in its SM2 housing.}
    \label{sfig8}
\end{figure}
%
\subsection{Scan lens assembly}
The scan lens assembly is shown in Fig.~\ref{sfig8}C. The individual steps for the scan lens group are as follows:
\begin{itemize}
    \item Place the KPC070AR, a plano-concave lens, on the spanner wrench with the plane side facing out. Check the lens thoroughly for dust and finger prints.
    \item Slide the SM2 tube over the elements until they sit at the end of the tube. Sometimes it needs to be wiggled, to make sure the lenses are seated properly.
    \item Flip the whole thing over.
    \item Tighten it with a SM2 retaining ring.
    \item Next, place the LB1199-B lens on the wrench. This is a bi-convex lens for which the orientation is irrelevant. Flip over the assembly, and tighten the lens with a second SM2 retaining ring. 
    \item For the third and fourth lens, place an ACT508-200-B lens, a spacer ring, the second ACT508-200-B lens, and two spacer rings on the wrench. Make sure you remove all dust from the various surfaces. Flip over the assembly, and tighten the lens with a third SM2 retaining ring. 
    \item Check the assembly for trapped dust or fingerprints. This will produce a lens group like the one shown in Fig.~\ref{sfig8}D.
\end{itemize}
